Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
edits to section 3 first two lemmas

	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
	\item Include explicit definitions for what we are assuming about a curve, i.e. smooth, projective, etc. Also, possibly discuss the relations to stacks, either here in or in the introduction. Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
	\item \begin{defn}
\label{}
If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}
\end{enumerate}

@@

\section{Inductive lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem, Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which describe the generators and relations of $R_{D + \frac{\alpha
}{\beta}P},$ given those in $R_D,$ 
where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$D \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. 
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

@@

Before proving three inductive lemmas, we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  \todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}

@@

Now, let $f\in T$.  Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \langle T \rangle.
\end{align*}

Next, suppose $f\in S$.  Note that by (2) any polynomial $G$ in $x_1,\ldots, x_m, y_1, \ldots, y_n$ with initial term in $S$ cannot have a term in $T$.  Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), any such polynomial does not map to an element of $R_{\halfcan'}$ (since it has a non-zero constant factor with $f$).  Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.  Therefore, 
\[
	\initial(I)\subseteq R_\halfcan-S.
\]

@@

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated $x_1, \ldots x_m$.  Then we have a map $\phi: k[z_1, \ldots z_m]\to R_\halfcan$ given by $z_i\mapsto x_i$.  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify that these satisfy the conditions of an ordering.

Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.

\begin{defn}\label{den:lower-approximation}
If $\frac{\alpha}{\beta}\in \BQ$ (written in reduced form with $\alpha \in \mathbb{Z}, \beta> \mathbb{N}$), then $\frac{c}{d}$ (written in reduced form) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there is no $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$. 
\end{defn}
Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
\[
	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
\]
Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.

\begin{figure}[H]\label{fig:s14/5-lattice}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure illustrates each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
\end{figure}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$ meaning that $R_{\halfcan'}$ has generators
$u, x_1, \ldots, x_m$ in degree at most $\sigma$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\begin{align*}
	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
										 + \langle U_i: 1 \le i \le n-1 \rangle
										 + \langle V \rangle\\
\end{align*}
where 
$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
 and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
\begin{enumerate}
	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
	\item[(2)] there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
\end{enumerate}

@@

\[
	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + d\frac{\alpha}{\beta}
\]

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will use positive best lower approximations to
construct the generators $\{y_i\}$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$ as described in this lemma's statement. Note that elements of $H^0(X, d\halfcan)$ have poles of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  Moreover, a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

For any $j, i \in \mathbb{N}$, with $i < j$, we have $\frac{c_i}{d_i} > \frac{c_j}{d_j}$. So, for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ \todo{are the $i$ and $j$ mismatched?} for all $z_j$, \todo{It might be clearer to say for all $j \in \{1,\ldots, ?\},$ since the subscript is really want is changing, or instead for all $j$ with $1 \leq j \leq ?$ } $\prod_{j=1}^n z_j$ must satisfy \todo{It seems like each $z_j$ must satisfy this, instead of the product satisfying this}
\todo{In the next equations, are we viewing these as rational functions on the structure sheaf or on $L'$, what point is the order of $z_j$ taken with respect to?}
\[
	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d_i},
\]

\noindent
so we have the pole order of $\prod_{j=1}^n z_j$ is \todo{what is the following sum taken over?}
\[
	\sum_{j=1}^n -\ord(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ and if $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
\beta}$ is not a best lower approximation. Then choose
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\[
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\]

This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

>>>>

	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
	\item Include explicit definitions for what we are assuming about a curve, i.e. smooth, projective, etc. Also, possibly discuss the relations to stacks, either here in or in the introduction. Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
	\item \begin{defn}
\label{}
If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
\end{defn}
\end{enumerate}

@@

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

@@

Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e. $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}

@@

Now, let $f\in T$.  Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \langle T \rangle.
\end{align*}

Next, suppose $f\in S$.  Note that by (2) any polynomial $G$ in $x_1,\ldots, x_m, y_1, \ldots, y_n$ with initial term in $S$ cannot have a term in $T$.  Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), any such polynomial does not map to an element of $R_{\halfcan'}$ (since it has a non-zero constant factor with $f$). \todo{Peter: Is this abuse of notation okay?} Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.  Therefore, 
\[
	\initial(I)\subseteq R_\halfcan-S.
\]

@@

To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
\begin{defn}
Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.  Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$. \todo{Do we need to instantiate the $z_i$.  If so, what is the best way to do so.  Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows: 
If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
\end{enumerate}
\end{defn}
\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.

Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}. \todo{Peter: This sentence is very ugly.  On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.  How should we state it better?  Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}

\begin{defn}\label{den:lower-approximation}
If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c\in \mathbb{Z}, d\in \mathbb{N}$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$. 
\end{defn}
Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
\[
	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
\]
Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.

\todo{Peter: Do we want this as an [H] figure; this seems a little non-standard and can create problems with display.  Nonetheless, I copied this format to match the figure in a later section}
\begin{figure}[H]\label{fig:s14/5-lattice}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
\end{figure}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\begin{align*}
	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
										 + \langle U_i: 1 \le i \le n-1 \rangle
										 + \langle V \rangle\\
\end{align*}
where 
$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
 and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}$ such that
\begin{enumerate}
	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
	\item[(2)] there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
\end{enumerate}

@@

\[
	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor
\]

\noindent
so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $\{y_i\}$ as described in the lemma's statement.

@@

\noindent
be the positive best lower approximations of $\frac{
\alpha}{\beta}$ as described in this lemma's statement. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
\[
	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
\]

\noindent
so
\[
	-\ord^{\halfcan'}_P(\prod_{j=1}^n z_j) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
\beta}$ is not a best lower approximation. Then choose a
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\[
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\]

Using this fact, we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
